# Illustrative Example: Predicting Risk of Ischemic Stroke



**Learning objectives:**

Understanding the computing part with two examples


## Introduction

Here we see how to make things in practice with two case studies.

## Example 1

Code for Ischemic Stroke case study.
Code requires these packages, across all of Chapter 2:

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-1, message=FALSE, warning=FALSE, paged.print=FALSE}
library(corrplot)
library(utils)
library(pROC)
library(plotly)
library(caret)
library(patchwork)
library(tidymodels)

theme_set(theme_bw())
```


Load the stroke_data.R.data from the Ischemic_Stroke folder here: https://github.com/topepo/FES/tree/master/Data_Sets

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-2}
load(url("https://github.com/topepo/FES/blob/master/Data_Sets/Ischemic_Stroke/stroke_data.RData?raw=true"))
load(url("https://github.com/topepo/FES/blob/master/02_Predicting_Risk_of_Ischemic_Stroke/stroke_rfe.RData?raw=true"))
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-3}
#pre_split data how many in each class by set
stroke_train %>% 
  count(Stroke) %>% 
  mutate(Data = "Training") %>% 
  bind_rows(
    stroke_test %>% 
      count(Stroke) %>% 
      mutate(Data = "Testing")
  ) %>% 
  spread(Stroke, n)
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-4}
#sampling using tidymodels/rsample package

all_stroke <- bind_rows(stroke_train, stroke_test) #put all the data back together

tidy_sample <- #sample, but fixing proportion of Stroke between test and train
	initial_split(all_stroke, prop = 0.71, strata = Stroke) 

tidy_testing <- testing(tidy_sample) #extract testing
tidy_training <- training(tidy_sample) #extract training

tidy_training %>% 
  count(Stroke) %>% 
  mutate(Data = "Training") %>% 
  bind_rows(
    tidy_testing %>% 
      count(Stroke) %>% 
      mutate(Data = "Testing")
  ) %>% 
  spread(Stroke, n)
# distribution of training and testing is either exactly the same or one off depending on seed

```

### Predictor Quality

The first thing is to just look at your data:

- what's missing
- what's normal(ish)
- what's the range
- what's the data type

dplyr's glimpse is a good starting point.
```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-5}
dplyr::glimpse(tidy_training)
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-6}
# skimr is better (by a lot)
# https://github.com/ropensci/skimr
skimr::skim(all_stroke)
```



The book says original dataset has 4 missing data points, but already been median imputed via `recipes::step_impute_median()`
imputation methhods discussed more in Chapter 8, some models hate missing data

if you have missing data...
use naniar/visdat to visualize datasets and understand where you're missing data
[getting-started-w-naniar](https://cran.r-project.org/web/packages/naniar/vignettes/getting-started-w-naniar.html)


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-7, message=FALSE, warning=FALSE, paged.print=FALSE}
visdat::vis_dat(tidy_training)
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-8}
# https://bookdown.org/max/FES/numeric-one-to-one.html#numeric-one-to-one
# this is a plot of the distribution of MaxLRNCArea, very right skewed
fig_2_2_a <- 
  all_stroke %>% 
  ggplot(aes(x = MaxLRNCArea)) +
  geom_histogram(bins = 15, col = "#D53E4F", fill = "#D53E4F", alpha = .5) +
  xlab("MaxLRNCArea") +
  ylab("Frequency") +
  ggtitle("(a)") +
  theme_bw()

fig_2_2_a
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-9}
# same plot but after yeojohnson transformmation, become normal-like
fig_2_2_b <- 
  recipe(Stroke ~ ., data = all_stroke) %>% 
  step_YeoJohnson(all_predictors()) %>% 
  prep(.) %>% 
  bake(., new_data = NULL) %>% 
  ggplot(aes(x = MaxLRNCArea)) +
  geom_histogram(bins = 15, col = "#D53E4F", fill = "#D53E4F", alpha = .5) +
  xlab("Transformed MaxLRNCArea") +
  ylab("Frequency") +
  ggtitle("(b)") +
  theme_bw()

#sidebyside with patchwork
fig_2_2_a + fig_2_2_b
```

### understanding interactions and multicollinearity

some models hate correlated traits

this only looks at imaging traits, (why is it called risk?)

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-10}
risk_train <-
  recipe(Stroke ~ ., data = stroke_train) %>%
  step_center(all_of(VC_preds)) %>% # center the data
  step_scale(all_of(VC_preds)) %>% # scale the data
  step_YeoJohnson(all_of(VC_preds)) %>% # YeoJohnson transform https://recipes.tidymodels.org/reference/step_YeoJohnson.html
  prep(.) %>% 
  bake(., new_data = NULL) %>% # juice is superseded by bake
  select(-one_of(c("Stroke", "NASCET", risk_preds))) #select everything but these

risk_corr <- cor(risk_train) #make a correlation matrix

corrplot(risk_corr, addgrid.col = rgb(0, 0, 0, .05), order = "hclust") #plot that

```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-11}
# you can remove these with step_corr(all_predictors(), threshold = 0.75) %>% 
risk_train_step_corr <-
  recipe(Stroke ~ ., data = stroke_train) %>%
  step_center(all_of(VC_preds)) %>% # center the data
  step_scale(all_of(VC_preds)) %>% # scale the data
  step_YeoJohnson(all_of(VC_preds)) %>% # YeoJohnson transform https://recipes.tidymodels.org/reference/step_YeoJohnson.html
  step_corr(all_predictors(), threshold = 0.75) %>% # remove "extra" predictors with correlations higher than 0.75
  prep(.) %>% 
  bake(., new_data = NULL) %>% # juice is superseded by bake
  select(-one_of(c("Stroke", "NASCET", risk_preds))) #select everything but these

risk_corr_step_corr <- cor(risk_train_step_corr) #make a correlation matrix

corrplot(risk_corr_step_corr, addgrid.col = rgb(0, 0, 0, .05), order = "hclust") #plot that

#BUT WE'RE NOT DOING THAT YET! Chapter 3 shows more methods on this.

```


## Example 2

Code for Section 2.4 at
https://bookdown.org/max/FES/stroke-tour.html#stroke-exploration


Code to compare 2-way interaction models to their main effects model

`a` and `b` are two models from `train()`

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-12}
compare_models_1way <- function(a, b, metric = a$metric[1], ...) {
  mods <- list(a, b)
  rs <- resamples(mods)
  diffs <- diff(rs, metric = metric[1], ...)
  diffs$statistics[[1]][[1]]
}
```



`risk_preds` is contained in the original data file and has the predictor 
names for the risk related variables


### Create a "null model" with no predictors to get baseline performance

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-13, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
null_mat <- data.frame(intercept = rep(1, nrow(stroke_train)))

ctrl <- 
  trainControl(method = "repeatedcv", repeats = 5,
               classProbs = TRUE, 
               summaryFunction = twoClassSummary)

set.seed(63331)
null_mod <- train(x = null_mat, 
                  y = stroke_train$Stroke, 
                  preProc = "YeoJohnson",
                  method = "glm", 
                  metric = "ROC", 
                  trControl = ctrl)
```

Compare the models with single predictors to the risk model. These data make

https://bookdown.org/max/FES/stroke-tour.html#tab:stroke-strokeRiskAssociations

`VC_preds` and `risk_preds` contain the predictor names for different sets.

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-14, eval=TRUE}
one_predictor_res <- 
  data.frame(Predictor = c(VC_preds, risk_preds), 
             Improvement = NA,
             Pvalue = NA,
             ROC = NA,
             stringsAsFactors = FALSE)


for (i in 1:nrow(one_predictor_res)) {
  set.seed(63331)
  var_mod <- train(Stroke ~ ., 
                   data = stroke_train[, c("Stroke", one_predictor_res$Predictor[i])], 
                   method = "glm", 
                   metric = "ROC",
                   trControl = ctrl)  
  tmp_diff <- compare_models_1way(var_mod, 
                                  null_mod, 
                                  alternative = "greater")
  one_predictor_res$ROC[i] <- getTrainPerf(var_mod)[1, "TrainROC"]
  one_predictor_res$Improvement[i] <- tmp_diff$estimate
  one_predictor_res$Pvalue[i] <- tmp_diff$p.value
}
```



### With Tidymodels


attempting this with tidymodels, not exactly the same
need to make some sort of resample object to feed workflow_map
```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-15}

model_folds <- vfold_cv(tidy_training, v = 10, repeats = 5)
# model_boots <- bootstraps(tidy_training, times = 50) #want to bootstrap this?

#defining the null model
null_class_model <- 
	null_model() %>%
	set_engine("parsnip") %>%
	set_mode("classification")

null_model <- workflow_set(preproc = c(Stroke ~ .), 
                           models = list(null_mod = null_class_model))

```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-16}
# defining the model
lm_model <- 
  logistic_reg(
  mode = "classification", # outcome is a classification Stroke Y/N
  engine = "glm",	#using glm like the example
  penalty = NULL,	
  mixture = NULL		
)
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-17}
# make named list of single variable formulae
single_var_formulae <-
	c(VC_preds, risk_preds) %>%
	paste0("Stroke ~ ", .) %>%
	set_names(., c(VC_preds, risk_preds)) %>%
	as.list() %>%
	map(., as.formula)
```

Create the workflow set, all of our models use the same type of model and input data

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-18}

single_var_models <- workflow_set(preproc = single_var_formulae, 
                                     models = list(lm = lm_model))

all_models <- bind_rows(null_model, single_var_models)

# control grid/resamples allow processing of resampled data and parallel processing
# here we are asking only to save the predictions
control <- control_resamples(save_pred = TRUE)
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-19, eval=FALSE}
doParallel::registerDoParallel()
all_models1 <- 
	all_models %>%
	#map over each model and its resamples, use the control parameters, and be noisy
 	workflow_map(., 
 	             resamples = model_folds, 
 	             control = control, 
 	             verbose = TRUE)

# save(all_models1, file = "data/all_models1.RData", compress = "xz")
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-20, echo=FALSE}
load("data/all_models1.RData")
```



```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-21}
# per model what are the predictions, summmarize over resamples
collect_predictions(all_models1, summarize = TRUE)
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-22}
# per model what are the outputs in terms of fit (auc_roc) and accuracy 
collect_metrics(all_models1)
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-23}
# plot the output to show which individual parameters have the most impact
autoplot(
   all_models1,
   rank_metric = "roc_auc",  # <- how to order models
   metric = "roc_auc",       # <- which metric to visualize
   select_best = FALSE     # <- one point per workflow
) +
   geom_text(aes(y = mean - 1/10*mean, 
                 label = wflow_id),
             angle = 90, hjust = 1) +
   theme(legend.position = "none")
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-24}
# per model, sort by auc_roc
all_models1 %>%
rank_results() %>% 
   filter(.metric == "roc_auc")
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-25}
# Data in table 2.3
# https://bookdown.org/max/FES/stroke-tour.html#tab:stroke-strokeRiskAssociations

one_predictor_res %>% 
  dplyr::filter(Predictor %in% risk_preds) %>% 
  arrange(Pvalue)
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-26}
# Figure 2.4
# https://bookdown.org/max/FES/stroke-tour.html#fig:stroke-vascuCAPAssocations

vc_pred <- 
  recipe(Stroke ~ ., data = stroke_train %>% dplyr::select(Stroke, !!!VC_preds)) %>% 
  	step_YeoJohnson(all_predictors()) %>% 
  	prep(stroke_train %>% dplyr::select(Stroke, !!!VC_preds)) %>% 
  	bake(., new_data = NULL) %>% 
  	gather(Predictor, value, -Stroke)
vc_pred%>%head
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-27}
pred_max <- 
  vc_pred %>% 
  group_by(Predictor) %>% 
  summarize(max_val = max(value)) %>% 
  inner_join(one_predictor_res %>% dplyr::select(Pvalue, Predictor)) %>% 
  mutate(
    x = 1.5, 
    value = 1.25 * max_val,
    label = paste0("p-value: ", format.pval(Pvalue, digits = 2, sci = FALSE, eps = .0001))
  )
pred_max%>%head
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-28}
new_order <- pred_max$Predictor[order(pred_max$Pvalue)]

vc_pred <- 
  vc_pred %>% 
  mutate(Predictor = factor(Predictor, levels = new_order))

pred_max <- 
  pred_max %>% 
  mutate(Predictor = factor(Predictor, levels = new_order))

fig_2_4 <-
  ggplot(vc_pred, aes(x = Stroke, y = value)) + 
  geom_boxplot() + 
  geom_point(alpha = 0.3, cex = .5) + 
  geom_text(data = pred_max, aes(x = x, label = label), size = 3) + 
  facet_wrap(~Predictor, scales = "free_y") + 
  ylab("")
fig_2_4
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-29}
# Figure 2.5
# https://bookdown.org/max/FES/stroke-tour.html#fig:stroke-maxRemodelingRatioROC

fig_2_5 <- 
  roc_curve(stroke_train, Stroke, MaxRemodelingRatio) %>% 
  # used opposite values
  ggplot(aes(x = specificity, y = 1-sensitivity)) + 
  geom_abline(alpha = .5, lty = 2) +
  geom_path()

fig_2_5
```

### Interaction exploration


Here they create all the pairs of all of the image analysis components 
there are 171 interactions

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-30, eval=TRUE}
pairs <- 
  combn(VC_preds, 2) %>% 
  t() %>% 
  as.data.frame(stringsAsFactors = FALSE) %>% 
  mutate(
    Improvement = NA,
    Pvalue = NA,
    ROC = NA
  )
```

Run comparisons with caret

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-31, eval=FALSE,message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
for (i in 1:nrow(pairs)) {
  tmp_vars <- c("Stroke", pairs$V1[i], pairs$V2[i])
  set.seed(63331)
  main_eff <- train(Stroke ~ ., 
                    data = stroke_train[, tmp_vars], 
                    preProc = c("center", "scale", "YeoJohnson"),
                    method = "glm", 
                    metric = "ROC",
                    trControl = ctrl)
  set.seed(63331)
  main_int <- train(Stroke ~ (.)^2, 
                    data = stroke_train[, tmp_vars], 
                    preProc = c("center", "scale", "YeoJohnson"), 
                    method = "glm", 
                    metric = "ROC", 
                    trControl = ctrl)  
  tmp_diff <- compare_models_1way(main_int, main_eff, alternative = "greater")
  pairs$ROC[i] <- getTrainPerf(main_eff)[1, "TrainROC"]
  pairs$Improvement[i] <- tmp_diff$estimate
  pairs$Pvalue[i] <- tmp_diff$p.value
}
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-32, eval=FALSE,include=FALSE}
pairs1 <- pairs
# save(pairs1,file = "data/pairs1.RData")
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-33, echo=FALSE}
load("data/pairs1.RData")
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-34}
retained_pairs <- 
  pairs1 %>% 
  dplyr::filter(ROC > 0.5  & Pvalue <= 0.2)
retained_pairs%>%head
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-35, message=FALSE, warning=FALSE, paged.print=FALSE}
# Figure 2.6
# https://bookdown.org/max/FES/stroke-tour.html#fig:stroke-interactionScreening

vol_plot <- 
  pairs1 %>% 
  dplyr::filter(ROC > 0.5) %>%
  mutate(Term = paste(V1, "by", V2, "\nROC:", round(ROC, 2))) %>%
  ggplot(aes(x = Improvement, y = -log10(Pvalue))) + 
  xlab("Improvement") +
  geom_point(alpha = .2, aes(size = ROC, text = Term))

vol_plot <- ggplotly(vol_plot, tooltip = "Term")
vol_plot
```

Create interaction formula of things that matter most
```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-36}
int_form <- 
  pairs1 %>% 
  dplyr::filter(ROC > 0.5  & Pvalue <= 0.2 & Improvement > 0) %>% 
  mutate(form  = paste0(V1, ":", V2)) %>% 
  pull(form) %>% 
  paste(collapse = "+")

int_form <- paste("~", int_form)
int_form <- as.formula(int_form)
int_form%>%head
```


This part of the script is to work through all of of the potential models:

- original risk set alone
- imaging predictors alone
- risk and imaging predictors together
- imaging predictors and interactions of imaging predictors, and
- risk, imaging predictors, and interactions of imaging predictors 


All the models are run below.
```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-37}
risk_train <- 
  stroke_train %>%
  dplyr::select(one_of(risk_preds), Stroke)

risk_train%>%head
```
```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-38}
image_train <- 
  stroke_train %>%
  dplyr::select(one_of(VC_preds), Stroke)

image_train%>%head
```



```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-39 }
fiveStats <- function(...) c(twoClassSummary(...), defaultSummary(...))
internal_ctrl = trainControl(method = "none", classProbs = TRUE,
                             allowParallel = FALSE)
lrFuncsNew <- caretFuncs  
lrFuncsNew$summary <- fiveStats
rfeCtrl <- rfeControl(functions = lrFuncsNew,
                      method = "repeatedcv",
                      repeats = 5,
                      rerank = FALSE,
                      returnResamp = "all",
                      saveDetails = TRUE,
                      verbose = FALSE)

```


RFE procedure using risk predictors

All pair-wise interactions.
```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-40}
risk_int_filtered_recipe <-
  recipe(Stroke ~ ., data = risk_train) %>%
  step_interact(~ all_predictors():all_predictors()) %>%
  step_corr(all_predictors(), threshold = 0.75) %>% 
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_zv(all_predictors())
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-41, eval=FALSE}
set.seed(63331)
risk_int_filtered_rfe <- rfe(
  risk_int_filtered_recipe,
  data = risk_train,
  sizes = 1:36,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-42, eval=FALSE}
# Main effects
risk_main_filtered_recipe <-
  recipe(Stroke ~ ., data = risk_train) %>%
  step_corr(all_predictors(), threshold = 0.75) %>% 
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
risk_main_filtered_rfe <- rfe(
  risk_main_filtered_recipe,
  data = risk_train,
  sizes = 1:8,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)
```


RFE procedure using imaging predictors.
```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-43, eval=FALSE}
img_int_filtered_recipe <-
  recipe(Stroke ~ ., data = image_train) %>%
  step_interact(int_form)  %>%
  step_corr(all_predictors(), threshold = 0.75) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_YeoJohnson(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
img_int_filtered_rfe <- rfe(
  img_int_filtered_recipe,
  data = image_train,
  sizes = 1:35,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-44, eval=FALSE}
img_main_filtered_recipe <-
  recipe(Stroke ~ ., data = image_train)  %>%
  step_corr(all_predictors(), threshold = 0.75) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_YeoJohnson(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
img_main_filtered_rfe <- rfe(
  img_main_filtered_recipe,
  data = image_train,
  sizes = 1:19,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-45, eval=FALSE}
both_int_filtered_recipe <-
  recipe(Stroke ~ ., data = stroke_train) %>%
  step_interact(int_form)  %>%
  step_corr(all_predictors(), threshold = 0.75) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_YeoJohnson(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
both_int_filtered_rfe <- rfe(
  both_int_filtered_recipe,
  data = stroke_train,
  sizes = 1:44,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)

both_main_filtered_recipe <-
  recipe(Stroke ~ ., data = stroke_train)  %>%
  step_corr(all_predictors(), threshold = 0.75) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_YeoJohnson(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
both_main_filtered_rfe <- rfe(
  both_main_filtered_recipe,
  data = stroke_train,
  sizes = 1:28,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)

```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-46, eval=FALSE}
risk_int_recipe <-
  recipe(Stroke ~ ., data = risk_train) %>%
  step_interact(~ all_predictors():all_predictors()) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
risk_int_rfe <- rfe(
  risk_int_recipe,
  data = risk_train,
  sizes = 1:36,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)

```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-47, eval=FALSE}
risk_main_recipe <-
  recipe(Stroke ~ ., data = risk_train) %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
risk_main_rfe <- rfe(
  risk_main_recipe,
  data = risk_train,
  sizes = 1:8,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)

```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-48, eval=FALSE}
img_int_recipe <-
  recipe(Stroke ~ ., data = image_train) %>%
  step_interact(int_form)  %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_YeoJohnson(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
img_int_rfe <- rfe(
  img_int_recipe,
  data = image_train,
  sizes = 1:35,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)
```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-49, eval=FALSE}
img_main_recipe <-
  recipe(Stroke ~ ., data = image_train)  %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_YeoJohnson(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
img_main_rfe <- rfe(
  img_main_recipe,
  data = image_train,
  sizes = 1:19,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)

```



```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-50, eval=FALSE}
both_int_recipe <-
  recipe(Stroke ~ ., data = stroke_train) %>%
  step_interact(int_form)  %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_YeoJohnson(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
both_int_rfe <- rfe(
  both_int_recipe,
  data = stroke_train,
  sizes = 1:44,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)

both_main_recipe <-
  recipe(Stroke ~ ., data = stroke_train)  %>%
  step_center(all_predictors()) %>%
  step_scale(all_predictors()) %>%
  step_YeoJohnson(all_predictors()) %>%
  step_zv(all_predictors())

set.seed(63331)
both_main_rfe <- rfe(
  both_main_recipe,
  data = stroke_train,
  sizes = 1:28,
  rfeControl = rfeCtrl,
  metric = "ROC",
  ## train options
  method = "glm",
  trControl = internal_ctrl
)

```


```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-51}
format_data <- function(x, lab, int = FALSE) {
  dat <- 
    x %>% 
    pluck("results") %>% 
    mutate(Predictors = !!lab) %>% 
    dplyr::select(ROC, Variables, Predictors, Variables, Num_Resamples) %>% 
    mutate(Model = "Main Effects")
  if (int)
    dat$Model <- "Interactions"
  dat
  
}

filtered_dat <- 
  bind_rows(
    format_data(risk_main_filtered_rfe, lab = "Risk Predictors"),
    format_data(risk_int_filtered_rfe, lab = "Risk Predictors", TRUE),
    format_data(img_main_filtered_rfe, lab = "Imaging Predictors"),
    format_data(img_int_filtered_rfe, lab = "Imaging Predictors", TRUE),
    format_data(both_main_filtered_rfe, lab = "All Predictors"),
    format_data(both_int_filtered_rfe, lab = "All Predictors", TRUE)
  ) %>% 
  mutate(
    Predictors = factor(
      Predictors, 
      levels = c("Risk Predictors", "Imaging Predictors", "All Predictors")
    ),
    Model = factor(Model, levels = c("Main Effects", "Interactions")),
    Filtering = "Correlation Filter"
  )

unfiltered_dat <- 
  bind_rows(
    format_data(risk_main_rfe, lab = "Risk Predictors"),
    format_data(risk_int_rfe, lab = "Risk Predictors", TRUE),
    format_data(img_main_rfe, lab = "Imaging Predictors"),
    format_data(img_int_rfe, lab = "Imaging Predictors", TRUE),
    format_data(both_main_rfe, lab = "All Predictors"),
    format_data(both_int_rfe, lab = "All Predictors", TRUE)
  ) %>% 
  mutate(
    Predictors = factor(
      Predictors, 
      levels = c("Risk Predictors", "Imaging Predictors", "All Predictors")
    ),
    Model = factor(Model, levels = c("Main Effects", "Interactions")),
    Filtering = "No Filter"
  )

rfe_data <- 
  bind_rows(filtered_dat, unfiltered_dat) %>% 
  mutate(
    Filtering = factor(Filtering, levels = c("No Filter", "Correlation Filter"))
  )

```




```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-52}
# https://bookdown.org/max/FES/predictive-modeling-across-sets.html#fig:stroke-rfe-res
ggplot(rfe_data, aes(x = Variables, y = ROC, col = Model)) +
  geom_point(size = 0.75) + 
  geom_line() + 
  facet_grid(Filtering ~ Predictors) + 
  scale_color_manual(values = c("#6A3D9A", "#CAB2D6"))
```

```{r 02-illustrative-example-predicting-risk-of-ischemic-stroke-53}
# https://bookdown.org/max/FES/predictive-modeling-across-sets.html#tab:stroke-rfe-tab
rfe_tab <-
  img_main_filtered_rfe %>% 
  pluck("variables") %>% 
  filter(Variables == img_main_filtered_rfe$optsize) %>% 
  group_by(var) %>% 
  count() %>% 
  arrange(desc(n)) %>% 
  mutate(final = ifelse(var %in% img_main_filtered_rfe$optVariables, "Yes", "No")) %>% 
  ungroup()

```


## Meeting Videos

### Cohort 1

`r knitr::include_url("https://www.youtube.com/embed/0j-2e2bKMwM")`

<details>
<summary> Meeting chat log </summary>

```
00:17:23	Ben G:	Have to jump into a work call O
00:17:31	Ben G:	I'll jump back in later
00:17:33	Federica Gazzelloni:	@Brandon can you put it a little bit bigger?
00:21:39	Federica Gazzelloni:	even a little bit more
01:07:05	Ricardo Serrano:	https://recipes.tidymodels.org/articles/Ordering.html
01:08:02	Federica Gazzelloni:	thanks!
```
</details>
